### 2024-02-20 documentation/thesis/thesis_document.tex
.

This is important in order to understand the needs of the target group
and design the result accordingly. For this purpose, these were defined
into the following blocks:

@@

The selection process for possible magnetic field sensors initially
focuses on the most common and cost-effective ones, especially those
that are already used in smartphones and are therefore widely available.

@@

@@

The developed framework is directly compatible with a variety of
magnetic field sensors without modifications, including those listed in
the table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}.

@@

The values in table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
were taken from the data sheets of the relevant manufacturers as a
reference for comparison with the later measurement results.

This selection is made for the following reasons:

@@

The following parameters were determined and analysed for the sensor
evaulation:

@@

The characterisation methodology was modified and adapted from
Crescentini,Gibiino and Piero \customcite{CSG22}, as their approaches are
geared towards the analysis of analogue Hall sensors. Direct
transmission is not possible, as their methods are specially tailored to
these sensors. This includes measuring the analogue bias currents and
raw sensor output voltages, which are not accessible with these
digital-only sensors. Adaptations were therefore necessary to extend the
characterisation to the choosen digital sensors
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}.

@@

The setup is placed and pre-wired in the temperature chamber 24 hours
before the series of measurements are carried out. The insulated housing
of a \emph{Voron 2.4} 3D printer, which has a separately controlled
internal equipped heating system, is used as the temperature chamber. To
verify the temperature, an additional thermometer \emph{VC-7055BT} is
placed on the base plate. A \emph{10mm} thick \emph{PTFE} insulation
plate is placed between the floor and the sensor base plate to prevent
direct and uneven heating of the base plate by the heated floor.

@@

\hypertarget{sensor-characterisation-backgroundnoise}{%
\section{Sensor Characterisation:
BackgroundNoise}\label{sensor-characterisation-backgroundnoise}}

@@

The procedure starts with the acquisition of the baseline by operating
the sensor without external magnetic fields. For this purpose, a sample
size of \emph{\(N_{baseline}\)=10000} measured values is recorded for
the baseline measurement. The output signal of the sensor is
continuously measured and recorded. It is important to carry out the
measurement over a sufficiently lengthy period of time in order to
record both short-term and long-term fluctuations. For this purpose,
\emph{\(N_{measurement}\)=2000} further measured values are taken with a
trigger and readout rate of one measurement per second. In order to
quantify the noise, the \gls{sd} of the signal is calculated. These
parameters provide information about the variation of the signal over
time and therefore about the sensor background noise.

@@

\begin{itemize}
\tightlist
\item
  Plot of the raw data of the sensor
\item
  Plot of the sensor's internal temperature sensor
\item
  Background noise level with reference to the initial baseline
\item
  Histogram of the background noise level
\end{itemize}

@@

The temperature stability of the \emph{TLV493D} with a mean value of
20.68\(^{\circ}\)C and a \gls{sd} of \(\sigma_{t}\)=0.53\(^{\circ}\)C
indicates a consistent trend. This implies a constant tendency. The
close grouping of the measured values around the mean value indicates
good stability. The confidence interval is expected to be between
\emph{20.15\(^{\circ}\)C} and \emph{21.21\(^{\circ}\)C}, which indicates
a stable and consistent temperature measurement. This result is noisier
compared to the temperature stability of the \emph{MMC5603}.

Both sensors provide an offset to the measured chamber temperature
\(\mu_{trev}\).

@@

The noise of a sensor describes unwanted, random fluctuations or signals
in the measured data. These are clearly recognisable in the figure
\ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
in the raw data plot. The baseline measurement which was previously
determined for each sensor is shown by the red \(\mu_{rv}\)
{[}\(\mu\)T{]} line. It can be seen that each sensor has a different
baseline offset in the same environment. This variable is the result of
multiple effects, including the electrical offset introduced by the
front end and the effect of the earth's magnetic field \customcite{CSG22}
and the test environment.

For verification, a reference measurement of the environment is carried
out with the calibrated \emph{Voltcraft GM70} Telsameter next to the
sensor \gls{ic}. This provides a reference baseline value of
\emph{\(\mu_{rev}\)=-21.0\(\mu\)T}.

The noise of the sensor is drawn around this using the blue line. For
the \emph{TLV493D} the \gls{sd} \emph{\(\sigma_{rv}\)=172.0\({\mu}\)T},
which is twice the value given by the datasheet as the noise value
(refer to table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}).
Under the same conditions, the \emph{MMC5603NJ} undercuts the value
specified by the manufacturer. The \gls{sd} approaches
\emph{\(\sigma_{rv}\)=0.20\({\mu}\)T} and is negligible, especially when
additional averaging is used.

@@

@@

This is achieved by means of an additional linear axis installed above
the sensor setup. A holder for an \emph{N45 12x12x12mm} magnet is
attached to the end effector of this axis, which can thus be moved at
different distances above the respective sensor \gls{ic}. The ambient
temperature is set to \emph{\(\mu_{trev}\)=21.0\(^{\circ}\)C} in the
measurement runs and thus corresponds to the same conditions as in the
\emph{Background Noise} chapter
\ref{sensor-characterisation-background-noise} setup.

@@

In addition, the \gls{dr} for both sensors was measured before the
measurement run to determine the linearity. In this case, this indicates
the minimum and maximum linear measuring range for the selected linear
Hall sensors. A high \gls{dr} enables a more precise detection of
magnetic fields, while a low \gls{dr} can lead to the sensor detecting
magnetic fields outside its detection range \customcite{CSG22}.

@@

The figure
\ref{Sensor_linearity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
combines the visual representation of linearity as a plot. The distance
from the magnet to the sensor is plotted in \emph{mm} on the x-axis. The
measured value of the sensor is plotted on the y-axis. This is not
directly comparable for both plots, as the sensors have different
measuring ranges. To ensure comparability, the ideal curve is
determined. In order to be able to make quantifiable statements about
the measurement results, the mean and \gls{sd} deviation of these two
curves is determined.

@@

As the temperature sensor \emph{TLV493D} in particular produced vastly
different results in the previous measurements, an additional
temperature sensor is attached to the sensor circuit board for this
measurement. The figure
\ref{Sensor_evaluation_setup_for_temperature_sensitivity_measurements.png}
represents these modifications in detail. These changes makes it
possible to accurately determine the sensors \gls{ic} temperature. The
temperature measuring device \emph{VC-7055BT} can be analysed using a
\gls{pc} interface. The controller of the temperature chamber can also
be programmed via a \gls{pc} interface and a target temperature can be
specified.

@@

The field of permanent magnets is very temperature-dependent and can
lose its magnetisation at higher temperatures (typically
\emph{\textgreater=80\(^{\circ}\)} for non-high-quality type N magnets
\customcite{GKT16}). The temperature range is selected so that it is
within a sufficient range for the application.

@@

This thesis describes the development of a \gls{mrp} Python library that
can be used to efficiently process data from magnetic field sensors from
acquisition to analysis. To ensure a practical application and allow
users to acquire their own magnetic field data directly, a low-cost and
easily reproducible hardware is also developed. The hardware is based on
widely used consumer magnetic field sensors and low-cost
microcontrollers, enabling an easily expandable and applicable solution
for measuring magnets with repeatable accuracy. Special attention is
paid to the expandability by the user. Interchangeable modules allow the
user to develop their own analysis algorithms without having to design
everything from scratch. The software framework was evaluated on the
basis of the previously defined use cases. A user-defined sorting
algorithm was implemented and integrated into the framework. The result
is a list of the magnets that deviate least from the magnetic strength.

The result was successfully verified by means of manual checks for
various other series of measurements. In this way, extensibility and
customisability were also successfully demonstrated during the software
evaluation. This underlines the power of the developed framework and
shows that it is not only effective in processing magnetic field sensor
data, but also provides a flexible platform for the implementation of
user-specific analyses. Subsequently, the developed framework was used
to automatically characterise various magnetic field sensors. For this
purpose, the developed pipeline feature of the software was used to
determine various sensor characteristics, including background noise,
temperature coefficients and linearity.

@@

With this version of the framework, a solid basis has been created that
contains all the necessary functions to solve various problems in the
acquisition and processing of magnetic fields. Easy-to-assemble
measurement hardware has created an easy-to-use platform for the
characterisation of permanent magnets, for example. An exemplary
characterisation of the magnetic field sensors used allows the possible
areas of application for these to be narrowed down. The framework has
already been published in a first stable version, but extensions and
improvements are still necessary. The stable version is also distributed
via a package registration and can therefore be quickly evaluated by new
users. In addition, further user experience and actual measurements
under real laboratory conditions on \gls{mri} B0 field magnets are still
missing. This is limited by the currently restricted selection of
characterised sensors. The aim for the next revision of the hardware and
software framework is therefore to support additional magnetic field
sensors. The current restriction to purely digital sensor interfaces is
also to be extended to analogue interfaces. This will open up the use of
a wide range of magnetic field sensors. It is also possible to integrate
high-resolution magnetic field probes based on NMR samples, which can
cover measurement errors of less than \emph{10nT} in fields of more than
\emph{1T} \customcite{DBN08}. Another possibility already supported by the
software, but for which hardware development is still necessary, is 2D
arrays of magnetic field sensors to display fields on a
surface\customcite{CP16}. This means that deviations can also be
visualised graphically without physically moving the senso such as in
the implemented \emph{3D: Full Sphere} \ref{d-full-sphere} sensor. In
addition, larger areas or volumes, such as in a large \emph{B0} field,
can be measured more quickly.

>>>>

This is important in order to understand the needs of the target group
and design the result accordingly. For this purpose, these are defined
into the following blocks:

@@

The selection process for possible magnetic field sensors initially
focuses on the most common and cost-effective hall effect ones,
especially those that are already used in smartphones and are therefore
widely available to consumers.

\begin{figure}
\centering
\includegraphics{./generated_images/border_Typical_block_diagram_of_a_digital_hall_sensor_sensing_chain_using_three_hall_plates.png}
\caption{Typical block diagram of a digital hall sensor sensing chain
using three hall plates
\label{Typical_block_diagram_of_a_digital_hall_sensor_sensing_chain_using_three_hall_plates.png}}
\end{figure}

A Hall effect sensor utilises the Hall effect that occurs when current
flows in a conductor through which a magnetic field passes. The sensor
consists of a semiconductor material such as gallium arsenide or indium
antimonide. Inside the sensor are Hall effect plates, which essentially
consist of a thin layer of this semiconductor material \customcite{BJJ16}.

@@

Another point that contributed to the selection of this module is the
availability of the sensor \gls{ic}s as a ready-made and readily
available evaluation module. This ensured that the electrical design is
verified by the manufacturer so that the sensor could be operated with
the correct electrical parameters. On the other hand, it is possible to
evaluate several sensors in a shorter time, as a separate \gls{pcb} has
to be produced here.

@@

@@

The values in table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
are taken from the data sheets of the relevant manufacturers as a
reference for comparison with the later measurement results.

@@

The following parameters are determined and analysed for the sensor
evaulation:

@@

The characterisation methodology is modified and adapted from
Crescentini, Gibiino and Piero \customcite{CSG22}, as their approaches are
focused towards the analysis of analogue Hall sensors. Direct
transmission is not possible, as their methods are specially tailored to
these sensors. This includes measuring the analogue bias currents and
raw sensor output voltages, which are not accessible with these
digital-only sensors. Adaptations are therefore necessary to extend the
characterisation to the choosen digital sensors
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}.

@@

The set-up is set up and pre-wired in the temperature chamber \emph{24}
hours before the measurement series is performed. The insulated housing
of a \emph{Voron 2.4} 3D printer, which has a separately controlled
internal equipped heating system, is used as the temperature chamber. To
verify the temperature, an additional thermometer \emph{7055BT} is
placed on the base plate. A \emph{10mm} thick \emph{PTFE} insulation
plate is placed between the floor and the sensor base plate to prevent
direct and uneven heating of the base plate by the heated floor.

@@

\hypertarget{sensor-characterisation-background-noise}{%
\section{Sensor Characterisation: Background
Noise}\label{sensor-characterisation-background-noise}}

@@

The procedure starts with the acquisition of the baseline by operating
the sensor without external magnetic fields. For this purpose, a sample
size of \emph{\(N_{baseline}\)=10000} measured values is recorded for
the baseline measurement. The output signal of the sensor is
continuously measured and recorded. It is important to carry out the
measurement over a sufficiently lengthy period of time in order to
record both short-term and long-term fluctuations. For this purpose,
\emph{\(N_{measurement}\)=2000} additional measured values are taken
with a trigger and readout rate of one measurement per second. In order
to quantify the noise, the \gls{sd} of the signal is calculated. These
parameters provide information about the variation of the signal over
time and therefore about the sensor background noise.

@@

\begin{itemize}
\tightlist
\item
  Plot of the raw data of the sensor
\item
  Plot of the sensor's internal temperature sensor
\item
  Noise level with reference to the initial baseline
\item
  Histogram of the background noise level
\end{itemize}

@@

The temperature stability of the \emph{TLV493D} with a mean value of
20.68\(^{\circ}\)C and a \gls{sd} of
\(\sigma_{t,tlv}\)=0.53\(^{\circ}\)C indicates a consistent trend. This
implies a constant tendency. The close grouping of the measured values
around the mean value indicates good stability. The confidence interval
is expected to be between \emph{20.15\(^{\circ}\)C} and
\emph{21.21\(^{\circ}\)C}, which indicates a stable and consistent
temperature measurement. This result is noisier compared to the
temperature stability of the \emph{MMC5603} with stable
\emph{19.40\(^{\circ}\)C} with an accuracy of two decimal places.

Both sensors provide an offset to the measured chamber temperature
\(\mu_{trev, 7055BT}\).

@@

The noise of a sensor describes unwanted, random fluctuations or signals
in the measured data. These are clearly recognisable in the figure
\ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
in the raw data plot. The baseline measurement which is previously
determined for each sensor is shown by the red \(\mu_{rv}\)
{[}\(\mu\)T{]} line. It can be seen that each sensor has a different
baseline offset in the same environment. This variable is the result of
multiple effects, including the electrical offset introduced by the
front end and the effect of the earth's magnetic field \customcite{CSG22}
and the test environment.

For verification, a reference measurement of the environment is carried
out with the calibrated \emph{Voltcraft GM70} Telsameter next to the
sensor \gls{ic}. This provides a reference baseline value of
\emph{\(\mu_{rev, GM70}\)=-21.0\(\mu\)T}.

The noise of the sensor is drawn around this using the blue line. For
the \emph{TLV493D} the \gls{sd}
\emph{\(\sigma_{rv,tlv}\)=172.0\({\mu}\)T}, which is twice the value
given by the datasheet as the noise value (refer to table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}).
Under the same conditions, the \emph{MMC5603NJ} undercuts the value
specified by the manufacturer. The \gls{sd} approaches
\emph{\(\sigma_{rv, mmc}\)=0.20\({\mu}\)T} and is negligible, especially
when additional averaging is used.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Sensor_evaluation_setup_for_linearity_measurements.png}
\caption{Sensor evaluation setup for linearity measurements
\label{Sensor_evaluation_setup_for_linearity_measurements.png}}
\end{figure}

@@

This is achieved by means of an additional linear axis installed above
the sensor setup. A holder for an \emph{N45 12x12x12mm} magnet is
attached to the end effector of this axis, which can thus be moved at
different distances above the respective sensor \gls{ic}. The ambient
temperature is set to \emph{\(\mu_{trev, 7055BT}\)=21.0\(^{\circ}\)C} in
the measurement runs and thus corresponds to the same conditions as in
the \emph{Background Noise} chapter
\ref{sensor-characterisation-background-noise} setup.

@@

In addition, the \gls{dr} for both sensors are measured before the
measurement run to determine the linearity. In this case, this indicates
the minimum and maximum linear measuring range for the selected linear
Hall sensors. A high \gls{dr} enables a more precise detection of
magnetic fields, while a low \gls{dr} can lead to the sensor detecting
magnetic fields outside its detection range \customcite{CSG22}.

@@

The figure
\ref{Sensor_linearity_evaluation_results_for_TLV493D_and_MMC5603NJ.png}
combines the visual representation of linearity as a plot. The distance
from the magnet to the sensor is plotted in \emph{mm} on the x-axis. The
measured value of the sensor is plotted on the y-axis. This is not
directly comparable for both plots, as the sensors have different
measuring ranges. To ensure comparability, the ideal curve is determined
\customcite{CSG22}. In order to be able to make quantifiable statements
about the measurement results, the mean and \gls{sd} deviation of these
two curves is determined.

@@

As the temperature sensor \emph{TLV493D} in particular produced vastly
different results in the previous measurements, an additional
temperature sensor is attached to the sensor circuit board for this
measurement. The figure
\ref{Sensor_evaluation_setup_for_temperature_sensitivity_measurements.png}
represents these modifications in detail. These changes makes it
possible to accurately determine the sensors \gls{ic} temperature. The
temperature measuring device \emph{7055BT} can be analysed using a
\gls{pc} interface. The controller of the temperature chamber can also
be programmed via a \gls{pc} interface and a target temperature can be
specified.

@@

The field of permanent magnets is high temperature-dependent and can
lose its magnetisation at higher temperatures (typically
\emph{\textgreater=80\(^{\circ}\)} for non-high-quality \emph{Type-N}
magnets \customcite{GKT16}). The temperature range is selected so that it
is within a sufficient range for the application.

@@

This thesis describes the development of a \gls{mrp} Python library that
can be used to efficiently process data from magnetic field sensors from
acquisition to analysis. To ensure a practical application and allow
users to acquire their own magnetic field data directly, a low-cost and
easily reproducible hardware is also developed. The hardware is based on
widely used consumer magnetic field sensors and low-cost
microcontrollers, enabling an easily expandable and applicable solution
for measuring magnets with repeatable accuracy. Special attention is
paid to the expandability by the user. Interchangeable modules allow the
user to develop their own analysis algorithms without having to design
everything from scratch. The software framework is evaluated on the
basis of the previously defined use cases. A user-defined sorting
algorithm is implemented and integrated into the framework. The result
is a list of the magnets that deviate least from the magnetic strength.

The result is successfully verified by means of manual checks for
various other series of measurements. In this way, extensibility and
customisability are also successfully demonstrated during the software
evaluation. This underlines the power of the developed framework and
shows that it is not only effective in processing magnetic field sensor
data, but also provides a flexible platform for the implementation of
user-specific analyses. Subsequently, the developed framework is used to
automatically characterise various magnetic field sensors. For this
purpose, the developed pipeline feature of the software is used to
determine various sensor characteristics, including background noise,
temperature coefficients and linearity.

@@

With this version of the framework, a solid basis has been created that
contains all the necessary functions to solve various problems in the
acquisition and processing of magnetic fields. Easy-to-assemble
measurement hardware has created an easy-to-use platform for the
characterisation of permanent magnets, for example. An exemplary
characterisation of the magnetic field sensors used allows the possible
areas of application for these to be narrowed down. The framework has
already been published in a first stable version, but extensions and
improvements are still necessary. The stable version is also distributed
via a package registration and can therefore be quickly evaluated by new
users. In addition, further user experience and actual measurements
under real laboratory conditions on \gls{mri} B0 field magnets are still
missing. This is limited by the currently restricted selection of
characterised sensors. The aim for the next revision of the hardware and
software framework is therefore to support additional magnetic field
sensors. The current restriction to purely digital sensor interfaces is
also to be extended to analogue interfaces. This will open up the use of
a wide range of magnetic field sensors. It is also possible to integrate
high-resolution magnetic field probes based on NMR samples, which can
cover measurement errors of less than \emph{10nT} in fields of more than
\emph{1T} \customcite{DBN08}. Another possibility already supported by the
software, but for which hardware development is still necessary, is 2D
arrays of magnetic field sensors to display fields on a
surface\customcite{CP16}. This means that deviations can also be
visualised graphically without physically moving the sensors such as in
the implemented \emph{3D: Full Sphere} \ref{d-full-sphere} sensor. In
addition, larger areas or volumes, for example in a large \emph{B0}
field, can be measured more quickly.
